### 2021-03-31 notes/notes.tex
Added new likelihood description to notes

>>>>

\subsection{Context inference requires a new likelihood}
\label{subsec:new-likelihood}
It became clear by running preliminary simulations that, regardless of the
agent, context inference happened too quickly and too ``reliably''. The context
was identified during the first trial at first, and during deadaptation, when
the cue and the forces do not match, it took at most a couple of trials to
recognize the real context.

Since the model proposes that deadaptation is nothing but a consequence of slow
recognition of the context, lightning-fast context recognition will just not do
it.

The problem stems from the fact that the estimate on the magnitudes becomes so
good (e.g. low standard deviation on the estimate) that the likelihood
$p(x | C_t)$ becomes a delta function. Because of this, the cue itself is being
ignored and the context is immediately identified.

The best fix to this problem is to modify the way the likelihood works. As it
stands, the likelihood is the probability of observing the current hand position
given the current context and the previous hand position. The more ``separated''
the different estimates become from each other (the means are too far apart
and/or the precisions are too high), the more this is going to be a delta
function.

The best fix for this is to modify the likelihood function and introduce in it a
measurement of the reliability of each of the modalities of perception (force
feedback and visual cue). Such moderators are common in the literature
\citep[e.g.][]{Lee_Neural_2014}.

The simplest implementation I can think of is
one in which additive noise is added to the posterior estimate for each
modality:
\begin{equation}
p(C | \omega_t) \leftarrow (p(C | \omega_t) + \chi_{\omega})
p(C | s_{t-1}, s_t, a_{t-1}) \leftarrow (p(C |  s_{t-1}, s_t, a_{t-1}) + \chi_{\text{pred}})
\end{equation}
where $\chi_{\omega}$ and $\chi_{\text{pred}}$ are constants which encode the
reliability of each modality.

A more convoluted approach would be to bring all modalities to the same
level. In the current implementation, the likelihood uses the standard deviation
of the inference over the magnitudes to calculate $p(C | s, a)$. Instead, a
standard deviation could be used that is proportional to the mean, which would
put the cue and predictive modalities on the same playing ground, depending on
the proportionality constant chosen.
